---
title: "CARIT Public Release Data Report"
author: "John Flournoy"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    self_contained: false
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css?family=Didact+Gothic&display=swap');
@import url('https://fonts.googleapis.com/css?family=Fira+Code&display=swap');
body{
  font-family: 'Didact Gothic',  sans-serif;
}
pre code {
  font-family: 'Fira Code',  monospace;
}
```

```{r setup, include=FALSE}
library(showtext)
library(ggplot2)
library(data.table)
library(DT)
data.table::setDTthreads(2)

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#https://www.instagram.com/p/CCQvy_BAkWv/
apal <- paste0('#', c('005867', 'FFB335', 'F3F1EA', '2E383D', 'F34226'))

#{.tabset}
font_add_google("Didact Gothic", "Didact Gothic")
# showtext_auto()

jftheme <- theme_minimal() +  
  theme(text = element_text(family = 'Didact Gothic', size = 14),
        panel.background = element_rect(fill = apal[[3]], size = 0, color = apal[[2]]),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        strip.background = element_rect(fill = apal[[3]], size = 0),
        strip.text = element_text(color = apal[[1]]),
        axis.text =  element_text(color = apal[[4]]), axis.title = element_text(color = apal[[4]]))

dt_options <- list(rownames = FALSE,
                   filter = 'top',
                   class = 'cell-border stripe',
                   extensions = 'Buttons', 
                   options = list(dom = 'Bfrtip', buttons = c('csv')))

dt_table <- function(data, caption, dt_options = NULL){
  if(is.null(dt_options)){
    dt_options <- list(rownames = FALSE,
                   filter = 'top',
                   class = 'cell-border stripe',
                   extensions = 'Buttons', 
                   options = list(dom = 'Bfrtip', buttons = c('csv')))
  }
  return(do.call(DT::datatable, 
                 c(list(data,
                        caption = caption), 
                   dt_options)))
}

knitr::read_chunk('process_carit.R')
```

# Process data

```{r process_carit}
```

At the moment, there are 2 participants who have too many trials for one run. The raw data file indicates that the same conditions file was used for each one, but it also indicates that only 1 run was run. We may ultimately be able to use these cases but I'm setting them aside for now.

```{r}
#remove longitudinal subjects:
carit <- carit[!grepl('_V[2-9]_', filename),]
###INVESTIGATE FURTHER
duplicate_run_ids <- unique(carit[, .N, by = c('sID', 'runN')][N > 92, sID])
print(duplicate_run_ids)
dim(carit)
carit <- carit[!sID %in% duplicate_run_ids]
dim(carit)
carit_pr_scan <- carit[public_release, on = 'sID', nomatch = 0]
carit_pr_scan <- staged_dlmri[carit_pr_scan, on = 'sID'][has_carit == TRUE]
```

# Events

To model the BOLD using task behavior, we need to decide how to parse events.

We care primarily about how false alarms and correct rejections, but it would also be good to model out the go trials as well. We don't care too much about misses, and there likely will not be very many. Additionally, we might care about how many "Go" trials precede a "No-Go" trial. Finally, we are interested in how reward conditioning from a previously-run task impacts performance on "No-Go" trials.

FSL does not model the data all-at-once, though it does take into account variability at the first level. 

Refer: 

- https://www.fmrib.ox.ac.uk/datasets/techrep/tr04ss2/tr04ss2/node4.html

- https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FEAT

## Task basics

```{r}
#For each person:
#  get the number of events in each combination:
#     1. GO/NOGO
#     2. Prepotentcy POS/NEG

carit_pr_scan_trialtype_summary <- carit_pr_scan[, .N, by = c('sID', 'runN', 'corrRespTrialType')][corrRespTrialType != '']
trial_types <- data.table(expand.grid(sID = unique(carit_pr_scan$sID),
                                      corrRespTrialType = unique(carit_pr_scan$corrRespTrialType),
                                      runN = unique(carit_pr_scan$runN)))[corrRespTrialType != '']
carit_pr_scan_trialtype_summary <- carit_pr_scan_trialtype_summary[trial_types, on = c('sID', 'corrRespTrialType', 'runN')]
carit_pr_scan_trialtype_summary[, N := fifelse(is.na(N), 0, N)]

N_subs <- unique(carit_pr_scan_trialtype_summary[, 'sID'])[, .N]

no_trials_dt <- carit_pr_scan_trialtype_summary[N == 0][, list('N subjects' = .N,
                                                                   'Prop Subjects' = round(.N/N_subs, 2)), by = c('corrRespTrialType', 'runN')]

no_trials_dt[, corrRespTrialType := factor(corrRespTrialType, levels = c('Hit', 'Miss', 'corReject', 'falseAlarm')) ]

setkey(no_trials_dt, runN, corrRespTrialType)

lt3_trials_dt <- carit_pr_scan_trialtype_summary[N < 3][, list('N subjects' = .N,
                                                                   'Prop Subjects' = round(.N/N_subs, 2)), by = c('corrRespTrialType', 'runN')]

lt3_trials_dt[, corrRespTrialType := factor(corrRespTrialType, levels = c('Hit', 'Miss', 'corReject', 'falseAlarm')) ]

setkey(lt3_trials_dt, runN, corrRespTrialType)
```

```{r fig.width=7, fig.height=3}
carit_pr_scan_trialtype_summary[, c('N = 0') := factor(fifelse(N == 0, 'N == 0', 
                                                               fifelse(N < 3, 'N < 3', 'N >= 3')),
                                                       levels = c('N == 0', 'N < 3', 'N >= 3'))]
ggplot(carit_pr_scan_trialtype_summary, aes(x = N)) + 
  geom_histogram(aes(fill = `N = 0`), binwidth = 5) + 
  scale_fill_manual(values = apal[c(2, 5, 1)], name = '') + 
  facet_grid(runN ~ corrRespTrialType) + 
  jftheme
knitr::kable(no_trials_dt, 
             caption = sprintf('Number of participants without a particular trial type across all runs, out of N = %d',
                               N_subs))
knitr::kable(lt3_trials_dt, 
             caption = sprintf('Number of participants with < 3 events across all runs, out of N = %d',
                               N_subs))
```

## Prepotency

```{r}
carit_pr_scan_prepotency_summary <- carit_pr_scan[trialType == 'nogo'][, .N, 
                                                                         by = c('sID', 
                                                                                'runN',
                                                                                'corrRespTrialType',
                                                                                'prepotency')][corrRespTrialType != '']
trial_types_pp <- data.table(expand.grid(sID = unique(carit_pr_scan$sID),
                                         corrRespTrialType = unique(carit_pr_scan[trialType == 'nogo', corrRespTrialType]),
                                         prepotency = unique(carit_pr_scan[trialType == 'nogo', prepotency]),
                                         runN = unique(carit_pr_scan$runN)))[corrRespTrialType != '']
carit_pr_scan_prepotency_summary <- carit_pr_scan_prepotency_summary[trial_types_pp, on = c('sID', 'corrRespTrialType', 'runN', 'prepotency')]
carit_pr_scan_prepotency_summary[, N := fifelse(is.na(N), 0, N)]



no_trials_pp_dt <- carit_pr_scan_prepotency_summary[N == 0][, list('N subjects' = .N,
                                                                   'Prop Subjects' = round(.N/N_subs, 2)), by = c('corrRespTrialType', 'runN', 'prepotency')]


no_trials_pp_dt[, corrRespTrialType := factor(corrRespTrialType, levels = c('corReject', 'falseAlarm')) ]
no_trials_pp_dt[, prepotency := factor(prepotency)]

setkey(no_trials_pp_dt, runN, corrRespTrialType, prepotency)

lt3_trials_pp_dt <- carit_pr_scan_prepotency_summary[N < 3][, list('N subjects' = .N,
                                                                   'Prop Subjects' = round(.N/N_subs, 2)), by = c('corrRespTrialType', 'runN', 'prepotency')]

lt3_trials_pp_dt[, corrRespTrialType := factor(corrRespTrialType, levels = c('corReject', 'falseAlarm')) ]
lt3_trials_pp_dt[, prepotency := factor(prepotency)]

setkey(lt3_trials_pp_dt, runN, corrRespTrialType, prepotency)
```

```{r fig.width=6, fig.height=5}
carit_pr_scan_prepotency_summary[, c('N = 0') := factor(fifelse(N == 0, 'N == 0', 
                                                               fifelse(N < 3, 'N < 3', 'N >= 3')),
                                                       levels = c('N == 0', 'N < 3', 'N >= 3'))]
ggplot(carit_pr_scan_prepotency_summary, aes(x = N)) + 
  geom_histogram(aes(fill = `N = 0`), binwidth = 1) + 
  scale_fill_manual(values = apal[c(2, 5, 1)], name = '') + 
  scale_x_continuous(breaks = c(0:10)) + 
  facet_grid(runN + prepotency ~ corrRespTrialType) + 
  labs(x = 'Events', y = 'Number of Subjects') + 
  jftheme
knitr::kable(no_trials_pp_dt, 
             caption = sprintf('Number of participants without a particular trial type across all runs, out of N = %d', 
                               N_subs))
knitr::kable(lt3_trials_pp_dt, 
             caption = sprintf('Number of participants with < 3 events across all runs, out of N = %d',
                               N_subs))
```



# Misc Questions

What event time do we use for a correct rejection?

Prepotency: modeled as a factor, we have a lot of subjects with very few events. Should we collapse? Should we test linear, factorial effects? Can we do model comparison like this in FSL? What's the hypothesis we wish to test? Where is there a linear effect? Where is there a factorial effect? 


## Learning 

There's a learning component here we are not really accounting for. Does prepotency predict a no-go trial?

```{r}
num_fac <- function(x, levels = NULL){
  if(is.null(levels)){
    as.numeric(factor(x))  
  } else { 
    as.numeric(factor(x, levels = levels))
  }
}
lag1_num_fac_diff <- function(x, levels = NULL){
  y <- abs(num_fac(x, levels = levels) - num_fac(shift(x, fill = x[[1]], type = 'lag'), levels = levels))
  return(y)
}

trial_structure <- unique(carit_pr_scan[, c('runN', 'trialNum', 'prepotency', 'trialType')])

setorder(trial_structure, runN, trialNum)
trial_structure[, trial_type_diff := lag1_num_fac_diff(trialType, levels = c('go', 'nogo')), by = c('runN')]
trial_structure[, chunkID := cumsum(trial_type_diff)]
trial_structure[, N_of_trialType := 1:.N, by = c('runN', 'chunkID')]
trial_structure[, prev_trial := shift(trialType, type = 'lag'), by = c('runN')]
trial_structure[, is_nogo := as.numeric(trialType == 'nogo')]
trial_structure[, next_is_nogo := shift(is_nogo, n = 1, fill = NA, type = 'lead'), by = c('runN')]

trial_structure[, c('runN', 'trialNum', 'trialType', 'next_is_nogo', 'N_of_trialType')]
trial_structure <- trial_structure[trialType == 'go']

fit_b <- glm(next_is_nogo ~ N_of_trialType, data = trial_structure, family = 'binomial')
summary(fit_b)

with(trial_structure, table(N_of_trialType, next_is_nogo))
trial_structure[, list(P_nogo = sum(next_is_nogo)/.N), by = 'N_of_trialType']

#contrast
c <- contr.treatment(4)
my.coding <- matrix(rep(1/4, 12), ncol=3)
my.simple<- c - my.coding

trial_structure[, N_of_trialType_fac := factor(N_of_trialType)]
contrasts(trial_structure$N_of_trialType_fac) <- my.simple

fit_b_fac <- glm(next_is_nogo ~ N_of_trialType_fac, data = trial_structure)
summary(fit_b_fac)

#something something updating bayesian priors.
```

P(FA | Prepotency) across the trials

```{r}
modnum = 4
othernum = 24/modnum - 1
carit_pr_scan_learning <- carit_pr_scan[trialType == 'nogo']
setorder(carit_pr_scan_learning, 'sID', 'runN', 'trialNum')
carit_pr_scan_learning[, nogotrial := 1:.N, by = c('sID', 'runN')]
carit_pr_scan_learning[, nogotrial_group := (nogotrial - 1) %/% modnum]
carit_pr_scan_learning_summary <- carit_pr_scan_learning[, .(p_FA = mean(corrRespTrialType == 'falseAlarm', na.rm = TRUE),
                                                             N = .N), by = c('runN', 'nogotrial_group', 'prepotency')]
carit_pr_scan_learning_summary[, p_FA_SE := sqrt( p_FA * (1 - p_FA) / N)]
carit_pr_scan_learning_summary[, c('p_FA_u', 'p_FA_l') := list(p_FA + qnorm(.975) * p_FA_SE, p_FA + qnorm(.025) * p_FA_SE)]
```


```{r fig.width=5, fig.height=4}
ggplot(carit_pr_scan_learning_summary, aes(x = nogotrial_group, y = p_FA, group = prepotency, color = prepotency)) + 
  geom_errorbar(aes(ymin = p_FA_l, ymax = p_FA_u), width = 0) + 
  geom_point() + 
  geom_line() + 
  facet_grid( ~ runN) + 
  coord_cartesian(y = c(0, 1)) + 
  scale_x_continuous(breaks = 0:othernum, labels = sprintf('%d:%d', (0:othernum)*modnum+1, (0:othernum+1)*modnum)) + 
  scale_color_manual(values = apal[c(1,5,2)]) + 
  labs(x = 'Number of No-Go trials', y = 'Probability of a False-Alarm') +
  jftheme
```